Simulation-WTCCC

### 2019-11-22 analysis/simulation-WTCCC.Rmd
simu20191111

Here, $var(\tilde{X})$ is the cis-heratbility of gene expression. $M$ and $J$ are number of causal SNP and gene respectively.

@@

@@

### 1.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$
We set $\sigma_e=1$.

### 1.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

@@

### 2.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$
We set $\sigma_e=1$.

### 2.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

## Simulation 3: $M$ = ~ 10% all SNPs (M=50000), $J$ = No. all genes

### 3.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$ 
We set $\sigma_e=1$.

### 3.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

@@

### 4.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$ 
We set $\sigma_e=1$.

### 4.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

>>>>

Here, $var(\tilde{X})$ is the cis-heratbility of gene expression. $M$ and $J$ are numbers of causal SNP and gene respectively.

@@

```{r}
simudir <- "/home/simingz/causalTWAS/simulations/simulation_WTCCC_20191111/"
show_res <- function(simutag){
  load(Sys.glob(paste0(simudir,simutag,"*phenotype.Rd")))
  outdf1 <- data.frame(truth = c(sigma_gamma^2*J.c, sigma_theta^2*M.c , 1))
  row.names(outdf1) <- c("sigma_gamma^2","sigma_theta^2","sigma_e^2")
  res <- readLines(paste0(simudir, simutag, "_VC/output/", simutag, ".log.txt"))
  outdf1$est <- as.numeric(strsplit(res[24], "  ")[[1]][2:4])
  outdf1$est.se <- as.numeric(strsplit(res[25], "  ")[[1]][2:4])
  print(outdf1)
  outdf2 <- data.frame("est"= c(as.numeric(strsplit(res[20], "  ")[[1]][2:3]), as.numeric(strsplit(res[22], "=")[[1]][2])))
  row.names(outdf2) <- c("PVE.expr","PVE.snp","PVE.total")
  outdf2$est.se <- c(as.numeric(strsplit(res[21], "  ")[[1]][2:3]), as.numeric(strsplit(res[23], "=")[[1]][2]))
  print(outdf2)
}
```

@@

### 1.1 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.1$
```{r 1.1}
show_res("S1.1")
```

### 1.2 $PVE_{SNP}\approx 0.1$, $PVE_{expr}\approx 0.4$
```{r 1.2}
show_res("S1.2")
```

@@

### 2.1 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.1$
```{r 2.1}
show_res("S2.1")
```

### 2.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 2.2}
show_res("S2.2")
```
## Simulation 3: $M$ = ~ 10% all SNPs (M=50000), $J$ = No. all genes

### 3.1 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.1$ 
```{r 3.1}
show_res("S3.1")
```

### 3.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 3.2}
show_res("S3.2")
```

@@

### 4.1 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.1$ 
```{r 4.1}
show_res("S4.1")
```

### 4.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 4.2}
show_res("S4.2")
```
